Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2018-06-10 Conference/SCITECH19/SCITECH19.tex
merged TLee edits, updated gitignore

\begin{abstract}
This paper proposes a 3D autonomous exploration scheme designed for a flying vehicle to build a topological mapping the complex environment of the surface of Mars. 
The environment is modeled as a uniform grid, and the measurements from depth scans are utilized to determine the probability of occupancy at every cell within the scanned area. 
Shannon's entropy serves as a measure of map uncertainty, where the motion of the aerial vehicle is guided to minimize entropy, thereby maximizing map information. We propose a novel technique to predict future map entropy from depth sensors capable of scanning 3D spaces, and formulate autonomous exploration as an optimization problem based on map information gain subject to inequality constraints to void collision. The proposed approach is demonstrated with numerical simulations using contour data from the surface of Mars.
\end{abstract}

%\section{Nomenclature}
%
%{\renewcommand\arraystretch{1.0}
%\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
%$A$  & amplitude of oscillation \\
%$a$ &    cylinder diameter \\
%$C_p$& pressure coefficient \\
%$Cx$ & force coefficient in the \textit{x} direction \\
%$Cy$ & force coefficient in the \textit{y} direction \\
%c   & chord \\
%d$t$ & time step \\
%$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
%$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
%$f, g$   & generic functions \\
%$h$  & height \\
%$i$  & time index during navigation \\
%$j$  & waypoint index \\
%$K$  & trailing-edge (TE) nondimensional angular deflection rate
%\end{longtable*}}

@@

\section*{Acknowledgments}
This research has been supported in parts by the 2018 NASA Innovative Advanced Concepts (NIAC) award, and NSF under the grants CMMI-1243000, CMMI-1335008, CNS-1337722, and CMMI-1760928.

>>>>

\begin{abstract}
This paper proposes a 3D autonomous exploration scheme designed for a flying vehicle to build a topological map representing the complex environment of the surface of Mars. 
The environment is modeled as a uniform grid, and the measurements from depth scans are utilized to determine the probability of occupancy at every cell within the scanned area. 
Shannon's entropy serves as a measure of map uncertainty, where the motion of the aerial vehicle is guided to minimize entropy, thereby maximizing map information. We propose a novel technique to predict future map entropy from depth sensors capable of scanning 3D spaces, and formulate autonomous exploration as an optimization problem based on map information gain subject to inequality constraints to avoid collision. The proposed approach is demonstrated with numerical simulations using contour data from the surface of Mars.
\end{abstract}

@@

\section*{Acknowledgments}
This research has been supported by the 2018 NASA Innovative Advanced Concepts (NIAC) award and NSF under the grants CMMI-1243000, CMMI-1335008, CNS-1337722, and CMMI-1760928.
